---
title: "Text_Mining"
author: "Fereshteh Ahmadi, Seraina Felicitas Zimmermann, Michael Etter, Donjet Dzemaili"
format:
  html:
    df-print: paged
    toc: true
    code-tools: true

editor: visual
---

# Review Analysis for Disneyland

## Part 0: Prepossessing

### Environment and Setting

Please set your own virtual environment if needed

```{r}
#| label: choose_environment


reticulate::use_condaenv("huggingfaceR", required = TRUE)
set.seed(19)

```

### Libraries

Most of these are just libraries used by Lucia in her quarto docs, if not needed remove

```{r}
#| label: load_packages
#| message: false
#| warning: false
#| code-fold: true

library(tidyverse)            # Core data wrangling and visualization packages (dplyr, ggplot2, etc.)
library(quanteda)             # Text tokenization, preprocessing, and creating document-feature matrices
library(stopwords)            # Provides multilingual stopword lists for text cleaning
library(topicmodels)          # Topic modeling algorithms like LDA and CTM (Latent Dirichlet Allocation)
library(tidytext)             # Tidy-friendly tools for text mining and sentiment analysis
library(quanteda.textplots)   # Visualization tools for quanteda objects (word clouds, networks, etc.)
library(ggplot2)              # Grammar of graphics plotting system (used by tidyverse)
library(scales)               # Formatting and scaling functions for plots (e.g., percentages, dates)
library(devtools)             # Tools to install and manage R packages from GitHub
library(plotly)               # Interactive plots (works well with ggplot2 for interactivity)
library(readr)                # Efficient functions to read data (like CSVs) — part of tidyverse
library(ldatuning)            # Helps choose optimal number of topics in LDA models
library(bertopic)             # (If installed) R wrapper or interface to the Python BERTopic library
library(htmltools)            # Used in HTML report rendering and interactive outputs (like word clouds)
library(umap)                 # Uniform Manifold Approximation and Projection (UMAP) for dimensionality reduction
library(reticulate)

if (!require("cld2")) install.packages("cld2")
if (!require("hunspell")) install.packages("hunspell")
library(cld2) # for language detection
library(hunspell) # for spelling correction

options(scipen=999)



```

### Data

```{r}
load('Disneyland.rda')
head(reviews)


```

### Data tidying
A bit of cleaning...
```{r}

# Load stopwords
data("stop_words")

# remove symbols 
reviews_clean <- reviews %>%
  filter(!is.na(Review_Text)) %>%
  mutate(Review_ID,
         Review_Text = Review_Text %>%
           str_to_lower() %>%
           str_replace_all("http\\S+|www\\S+", "") %>%
           str_replace_all("<.*?>", "") %>%
           str_replace_all("[^a-z\\s]", " ") %>%
           str_squish()) 

custom_stops <- tibble(
  word = c("disney", "disneyland", "paris", "hong", "kong", "california", "ride", "rides", "park", "parks", "day")
)
all_stopwords <- bind_rows(stop_words, custom_stops)

# Step 2: Tokenize and remove stopwords
tokens <- reviews_clean %>%
  unnest_tokens(word, Review_Text) %>%
  anti_join(all_stopwords, by = "word")

# Step 3: Rebuild cleaned text from tokens and join back to full data
reconstructed <- tokens %>%
  group_by(Review_ID) %>%
  summarise(Review_Text_clean = str_c(word, collapse = " "), .groups = "drop")

# Step 4: Join back to original metadata
reviews_clean <- reviews_clean %>%
  left_join(reconstructed, by = "Review_ID")

```


-   **Multilingual Reviews:**

First we check and see if other languages are involved.

```{r}

# Detect language of each review
reviews$language <- detect_language(reviews$Review_Text)

# See if there are other languages in the data
reviews[reviews$language!= "en", ]


```
Since its difficult to fully recognize other languages we will use multilingual models.


-   **Fake or Sponsored Reviews:**

We also check and remove very short, identical and copy pasted reviews
```{r}
# very short reviews seem to be mostly 5 star ratings
reviews_clean %>% 
  mutate(word_count = str_count(Review_Text, "\\w+")) %>%
  arrange(word_count) %>%
  select(Rating, Review_Text, word_count) %>% 
  filter(word_count<10)

reviews_clean<-reviews_clean %>% 
  mutate(word_count = str_count(Review_Text, "\\w+")) %>%
  filter(word_count>10) %>% 
  group_by(Review_Text_clean) %>% 
    mutate(duplicate_count = n()) %>%
    ungroup() %>% 
    filter(duplicate_count == 1)


    
```

-   **Spelling Mistakes:**\

To solve this problem we mainly use NLPs.



## part 1: Content analysis and topic modeling

🔷 What can we tell about the customers that write reviews?

```{r}
# most of the customers write shorter reviews
reviews %>%
  mutate(length = nchar(Review_Text)) %>%
  ggplot(aes(x = length)) +
  geom_histogram(binwidth = 20)

```


Most of the reviews are for California and mostly from 2015-2017
```{r} 

# Extract year
reviews$year <- year(reviews$Year)

# Plot: Reviews by year and branch
reviews %>%
  count(year, Branch) %>%
  ggplot(aes(x = year, y = n, fill = Branch)) +
  geom_col(position = "dodge") +
  labs(title = "Review Counts by Year and Branch",
       x = "Year", y = "Number of Reviews") +
  theme_minimal()

```
seems like peek visits in California are in July, in Paris August and in HongKong December
```{r}
# Extract month (abbreviated names for labels)
reviews$month <- month(reviews$Year_Month, label = TRUE, abbr = TRUE)

# Plot: Reviews by month and branch
reviews %>%
  count(month, Branch) %>%
  ggplot(aes(x = month, y = n, fill = Branch)) +
  geom_col(position = "dodge") +
  labs(title = "Review Counts by Month and Branch",
       x = "Month", y = "Number of Reviews") +
  theme_minimal()

```
Seems like california has the lowest ratio of tourists who left a comment. 
```{r}
branch_country <- tibble::tibble(
  Branch = c("Disneyland_California", "Disneyland_Paris", "Disneyland_HongKong"),
  Country = c("United States", "France", "Hong Kong")
)

# Join to get park country
reviews_tagged <- reviews_clean %>%
  left_join(branch_country, by = "Branch") %>%
  mutate(Visitor_Type = if_else(Reviewer_Location == Country, "Local", "Tourist"))

reviews_tagged %>%
  count(Branch, Visitor_Type) %>%
  tidyr::pivot_wider(names_from = Visitor_Type, values_from = n, values_fill = 0) %>%
  mutate(Total = Tourist + Local,
         Tourist_Ratio = Tourist / Total)

```



## Part 2: Sentiment analysis

🔷 What do the visitors talk about in their reviews and how does it relate sentiment/ratings?


```{r}
set.seed(9) 

# Shuffle and sample the data
sampled_reviews <- reviews_tagged %>%
  filter(!is.na(Review_Text_clean)) %>%
  slice_sample(n = 10000) %>% 
  mutate(Review_Text_clean = str_trunc(Review_Text_clean, 450))  # about 512 tokens after tokenization

# Load Python's transformers package
transformers <- import("transformers")

# Load sentiment analysis pipeline
sentiment_model <- transformers$pipeline(
  task = "text-classification",
  model = "nlptown/bert-base-multilingual-uncased-sentiment"
)


# Enable tokenizer parallelism 
Sys.setenv(TOKENIZERS_PARALLELISM = "true")

emo_results <- sampled_reviews %>%
  mutate(
    sentiment = map(Review_Text_clean, safely(sentiment_model))
  ) %>%
  mutate(
    sentiment_result = map(sentiment, ~ .x$result[[1]]),
    stars = map_dbl(sentiment_result, ~ as.numeric(str_extract(.x$label, "\\d"))),
    label = case_when(
      stars <= 2 ~ "NEGATIVE",
      stars == 3 ~ "NEUTRAL",
      stars >= 4 ~ "POSITIVE"
    )
  )

# Disable parallelism again     
Sys.setenv(TOKENIZERS_PARALLELISM = "false")


 
```
ratings dont seem so good for paris
```{r}

emo_results %>%
  group_by(Branch) %>%
  summarise(avg_sentiment = mean(Rating, na.rm = TRUE))

```

Paris has many negative reviews why?
```{r}

sentiment_by_visitor <- emo_results %>%
  group_by(Branch, Visitor_Type, label) %>%
  summarise(count = n(), .groups = "drop")


sentiment_normalized <- sentiment_by_visitor %>%
  group_by(Branch, Visitor_Type) %>%
  mutate(percent = count / sum(count) * 100) %>%
  ungroup()


ggplot(sentiment_normalized, aes(x = Visitor_Type, y = percent, fill = label)) +
  geom_col(position = "dodge") +
  facet_wrap(~Branch) +
  labs(
    title = "Sentiment (%) by Visitor Type and Branch",
    x = "Visitor Type",
    y = "Percentage of Reviews",
    fill = "Sentiment"
  ) +
  theme_minimal()



```
Look at words or maybe cloud of words
```{r}

#| label: wordcloud

custom_stopwords <- c("disneyland", "disney", "park", "day")

# disneyland Paris
paris_tokens <- emo_results %>%
  filter(Branch == "Disneyland_Paris", label=="NEGATIVE", !is.na(Review_Text_clean)) %>%
  pull(Review_Text_clean) %>%
  tokens(
    remove_punct = TRUE,
    remove_numbers = TRUE,
    remove_symbols = TRUE
  ) %>%
  tokens_tolower() %>%
  tokens_remove(pattern = custom_stopwords)


paris_dfm <- dfm(paris_tokens)
paris_dfm <- paris_dfm[ntoken(paris_dfm) > 0, ]

textplot_wordcloud(
  paris_dfm,
  min_count = 10,
  max_words = 100,
  color = "darkblue",
  min_size = 0.5,
  max_size = 4
)


```
Lets use bertopic to find out what they are talking about
```{r}
# Load Python modules
bert <- import("bertopic")
sentence_transformers <- import("sentence_transformers")

# Embedding model (multilingual)
embedding_model <- sentence_transformers$SentenceTransformer("paraphrase-multilingual-MiniLM-L12-v2")

topic_model <- bert$BERTopic(
  embedding_model = embedding_model,
  nr_topics = r_to_py(6L),
  calculate_probabilities = TRUE,
  verbose = TRUE
)

docs <- emo_results %>%
  filter(Branch == "Disneyland_Paris", label == "NEGATIVE", !is.na(Review_Text_clean)) %>%
  slice_sample(n = 1000) %>%
  pull(Review_Text_clean)

# Fit model (run this in console, not inside Rmd chunk) it works for me though
topic_results <- topic_model$fit_transform(docs)

# Get summary of topics
topic_model$get_topic_info()






   
```

Lets visulize
```{r}

topic_info <- topic_model$get_topic_info()
topic_info_df <- py_to_r(topic_info)




topic_info_df %>%
  filter(Topic!=-1) %>% 
  ggplot(aes(x = reorder(Name, Count), y = Count, fill = Name)) +
  geom_col(show.legend = FALSE) +
  labs(title = "Frequency of Topics in Negative Disneyland Paris Reviews",
       x = "Theme", y = "Number of Reviews") +
  theme_minimal() +
  coord_flip()


```
```{r}

embeddings <- as.data.frame(py_to_r(topic_model$umap_model$embedding_)) 

colnames(embeddings) <- c("UMAP1", "UMAP2")
topics <- reticulate::py_to_r(topic_results[[1]])
embeddings$topics <- as.factor(topics)
# Remove NA-named columns
embeddings <- embeddings[, !is.na(names(embeddings)) & names(embeddings) != ""]

# Now safe to filter
embeddings <- embeddings %>% filter(topics != -1)


# trimming of outliers
ggplotly(
  ggplot(embeddings) +
    geom_point(aes(UMAP1, UMAP2, color = topics)) +
    theme_classic()
)


```


now lets do the same thing for California positive since they have the most positive reviews in our sample. 

```{r}


# Filter out text that appears more than once
emo_results <- emo_results %>%
  filter(duplicate_count == 1)

reviews_california_pos <- emo_results %>%
  filter(Branch == "Disneyland_California", label == "POSITIVE",  !is.na(Review_Text_clean)) %>%
  pull(Review_Text_clean)

reviews_california_pos <- reviews_california_pos %>%
  str_squish() %>%
  str_trunc(300)  # if input is long

# Use same embedding model as before
topic_model_california <- bert$BERTopic(
  embedding_model = embedding_model,
  min_topic_size = 30L,
  calculate_probabilities = TRUE,
  verbose = TRUE
)

topic_results_california <-topic_model_california$fit_transform(reviews_california_pos)
topic_model_california$get_topic_info()

topic_info_2 <- topic_model_california$get_topic_info()
topic_info_df_2 <- py_to_r(topic_info_2)




topic_info_df_2 %>%
  filter(Count >20, Topic!=-1) %>% 
  ggplot(aes(x = reorder(Name, Count), y = Count, fill = Name)) +
  geom_col(show.legend = FALSE) +
  labs(title = "Frequency of Topics in positive California Reviews",
       x = "Theme", y = "Number of Reviews") +
  theme_minimal() +
  coord_flip()




```

based on these insights, paris could work on negative topics and offer more fastpass, shows and events like firework, special attractions, friendlier staff and cleaner toilets.

## Part 3: Locations analysis

🔷 What differences can we detect for the three different locations and are there any interesting trends over time?

```{r}

```

## Part 4: Conclusion and Discussion

🔷 What specific advice can we give to the Park management based on our analysis? How can we integrate the analysis of reviews in internal processes, can we think of any data products that would be of value?
